Thermodynamic response functions in a cell fluid model

### 2024-07-22 main_morse_response_functions.tex
add thermal pressure coefficient figure

	\begin{figure}[h!]
		\centering \includegraphics[width=0.45\textwidth]{f2b.pdf}
		\includegraphics[width=0.475\textwidth]{f2c.pdf}
		\vskip-3mm\caption{The isothermal compressibility $K_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. The left-hand side figure covers a wider range of $M$, while the right-hand side one focuses on a range of $M$ around its critical value $0$.
		}\label{fig2b}
	\end{figure}

@@

>>>>

	\begin{figure}[h!]
		\centering \includegraphics[width=0.45\textwidth]{f2b.pdf}
		\includegraphics[width=0.475\textwidth]{f2c.pdf}
		\vskip-3mm\caption{The isothermal compressibility $K_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. The left-hand-side figure covers a wider range of $M$, while the right-hand-side one focuses on a range of $M$ around its critical value $0$.
		}\label{fig2b}
	\end{figure}

@@

	\begin{figure}[h!]
		\centering \includegraphics[width=0.5\textwidth]{f3.pdf}
		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
		}\label{fig3}
	\end{figure}
